---
title: "Cross-sectional models"
author: "Kate Tran"
date: "7/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(lme4)
library(readr)
library(sjPlot)

source("../utility_fun.R")
```

```{r}
data_wide <- read_csv("../outputs/data_wide_mm.csv")
```

# 1. Check association with CBCL
```{r}
diag_cbcl <- lmer(scale(CBCL_mean) ~ asthma_diagnosis_l_ever + scale(age_2y_years) + (1 | site_id_l_br/rel_family_id), data = data_wide)
diag_bpm <- lmer(scale(BPM_mean) ~ asthma_diagnosis_l_ever + scale(age_2y_years) + (1 | site_id_l_br/rel_family_id), data = data_wide)
tab_model(diag_cbcl, diag_bpm, show.intercept = F)
# Significant associations -> covary for CBCL, BPM
```

# 2. Model function
```{r}
var_mod_1 <- c(
  "scale(age_2y_years)",
  "sex_br",
  "race_white",
  "race_black",
  "race_other",
  "ethnicity_hisp",
  "(1 | site_id_l_br/rel_family_id)"
)

var_mod_2 <- c(
  var_mod_1,
  "scale(household_income)",
  "scale(parents_avg_edu)",
  "scale(devhx_3_p)"
)

var_mod_3 <- c(
  var_mod_2,
  "reshist_addr1_adi_perc",
  "scale(reshist_addr1_popdensity)",
  "scale(reshist_addr1_no2)",
  "scale(reshist_addr1_pm25)",
  "scale(reshist_addr1_proxrd)"
)
```

# 3.1. Outcome suicide attempt - asthma
## 3.1.1. Asthma diagnosis
```{r}
# SA_diag_0 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", 
#                              variables = "(1 | site_id_l_br/rel_family_id)"), 
#                       family = binomial, data = data_wide, nAGQ = 0)

SA_diag_1 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_1), 
                      family = binomial, data = data_wide, nAGQ = 0)

# SA_diag_2 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_2), 
#                       family = binomial, data = data_wide, nAGQ = 0)

SA_diag_3 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3), 
                      family = binomial, data = data_wide, nAGQ = 0)

# SA_diag_4 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
#                    family = binomial, data = data_wide, nAGQ = 0)

SA_diag_5 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                   family = binomial, data = data_wide, nAGQ = 0)

# comb_SA_diag_1 <- tab_model(SA_diag_0, SA_diag_1, SA_diag_2, SA_diag_3, SA_diag_4, SA_diag_5, show.intercept = F)
comb_SA_diag_1 <- tab_model(SA_diag_1, SA_diag_3, SA_diag_5, show.intercept = F, show.se = T, digits = 5)
comb_SA_diag_1
```

## 3.1.2. Asthma attack
```{r}
# SA_attack_0 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", 
#                               variables = "(1 | site_id_l_br/rel_family_id)"),
#                    family = binomial, data = data_wide, nAGQ = 0)

SA_attack_1 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_1), 
                   family = binomial, data = data_wide, nAGQ = 0)

# SA_attack_2 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_2), 
#                    family = binomial, data = data_wide, nAGQ = 0)

SA_attack_3 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3), 
                   family = binomial, data = data_wide, nAGQ = 0)

# SA_attack_4 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
#                    family = binomial, data = data_wide, nAGQ = 0)

SA_attack_5 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                   family = binomial, data = data_wide, nAGQ = 0)

# comb_SA_attack_1 <- tab_model(SA_attack_0, SA_attack_1, SA_attack_2, SA_attack_3, SA_attack_4, SA_attack_5, show.intercept = F)
comb_SA_attack_1 <- tab_model(SA_attack_1, SA_attack_3, SA_attack_5, show.intercept = F, show.se = T, digits = 5)
comb_SA_attack_1
```

## 3.1.3. Asthma composite
```{r}
# SA_comp_0 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_composite_ever", 
#                               variables = "(1 | site_id_l_br/rel_family_id)"), 
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# SA_comp_1 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_composite_ever", variables = var_mod_1), 
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# SA_comp_2 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_composite_ever", variables = var_mod_2), 
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# SA_comp_3 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_composite_ever", variables = var_mod_3), 
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# SA_comp_4 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_composite_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# SA_comp_5 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_composite_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# comb_SA_comp_1 <- tab_model(SA_comp_0, SA_comp_1, SA_comp_2, SA_comp_3, SA_comp_4, SA_comp_5, show.intercept = F)
# comb_SA_comp_1
```

## 3.1.4. Recently active asthma
```{r}
# SA_recent_active_0 <- glmer(get_models(outcome = "SA_y_ever", predictor = "recent_active_asthma_ever", 
#                               variables = "(1 | site_id_l_br/rel_family_id)"), 
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# SA_recent_active_1 <- glmer(get_models(outcome = "SA_y_ever", predictor = "recent_active_asthma_ever", variables = var_mod_1), 
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# SA_recent_active_2 <- glmer(get_models(outcome = "SA_y_ever", predictor = "recent_active_asthma_ever", variables = var_mod_2), 
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# SA_recent_active_3 <- glmer(get_models(outcome = "SA_y_ever", predictor = "recent_active_asthma_ever", variables = var_mod_3), 
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# SA_recent_active_4 <- glmer(get_models(outcome = "SA_y_ever", predictor = "recent_active_asthma_ever", 
#                                        variables = var_mod_3, var_added = "scale(CBCL_mean)"),
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# SA_recent_active_5 <- glmer(get_models(outcome = "SA_y_ever", predictor = "recent_active_asthma_ever", 
#                                        variables = var_mod_3, var_added = "scale(BPM_mean)"),
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# comb_SA_recent_active_1 <- tab_model(SA_recent_active_0, SA_recent_active_1, SA_recent_active_2, SA_recent_active_3, 
#                                      SA_recent_active_4, SA_recent_active_5, show.intercept = F)
# comb_SA_recent_active_1
```

## 3.1.5. Total number of asthma attacks/Mean number of mediation and SA #asthma_num_attack_sum #Asthma_medications_2w_total_sum
```{r}
Noattack_mean_SA_wholepop_1 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_num_attack_sum",
                                         variables = "(1 | site_id_l_br/rel_family_id)"), 
                              family = binomial, data = data_wide, nAGQ = 0)

Noattack_mean_SA_wholepop_2 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_num_attack_sum",
                                         variables = var_mod_1), 
                              family = binomial, data = data_wide, nAGQ = 0)

Nomedication_mean_SA_wholepop_1 <- glmer(get_models(outcome = "SA_y_ever", predictor = "Asthma_medications_2w_total_sum",
                                             variables = "(1 | site_id_l_br/rel_family_id)"), 
                                  family = binomial, data = data_wide, nAGQ = 0)

Nomedication_mean_SA_wholepop_2 <- glmer(get_models(outcome = "SA_y_ever", predictor = "Asthma_medications_2w_total_sum",
                                             variables = var_mod_1), 
                                  family = binomial, data = data_wide, nAGQ = 0)

tab_model(Noattack_mean_SA_wholepop_1, Noattack_mean_SA_wholepop_2, Nomedication_mean_SA_wholepop_1, Nomedication_mean_SA_wholepop_2, show.intercept = F)
```

# 4.1. Outcome suicide ideation - asthma
## 4.1.1. Asthma diagnosis
```{r}
# SI_diag_0 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", 
#                               variables = "(1 | site_id_l_br/rel_family_id)"), 
#                    family = binomial, data = data_wide, nAGQ = 0)

SI_diag_1 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_1), 
                   family = binomial, data = data_wide, nAGQ = 0)

# SI_diag_2 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_2), 
#                    family = binomial, data = data_wide, nAGQ = 0)

SI_diag_3 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3), 
                   family = binomial, data = data_wide, nAGQ = 0)

# SI_diag_4 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
#                    family = binomial, data = data_wide, nAGQ = 0)

SI_diag_5 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                   family = binomial, data = data_wide, nAGQ = 0)

# comb_SI_diag_1 <- tab_model(SI_diag_0, SI_diag_1, SI_diag_2, SI_diag_3, SI_diag_4, SI_diag_5, show.intercept = F)
comb_SI_diag_1 <- tab_model(SI_diag_1, SI_diag_3, SI_diag_5, show.intercept = F, show.se = T, digits = 5)
comb_SI_diag_1
```

## 4.1.2. Asthma attack
```{r}
# SI_attack_0 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", 
#                                 variables = "(1 | site_id_l_br/rel_family_id)"), 
#                      family = binomial, data = data_wide, nAGQ = 0)

SI_attack_1 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_1), 
                     family = binomial, data = data_wide, nAGQ = 0)

# SI_attack_2 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_2), 
#                      family = binomial, data = data_wide, nAGQ = 0)

SI_attack_3 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3), 
                     family = binomial, data = data_wide, nAGQ = 0)

# SI_attack_4 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
#                      family = binomial, data = data_wide, nAGQ = 0)

SI_attack_5 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                     family = binomial, data = data_wide, nAGQ = 0)

# comb_SI_attack_1 <- tab_model(SI_attack_0, SI_attack_1, SI_attack_2, SI_attack_3, SI_attack_4, SI_attack_5, show.intercept = F)
comb_SI_attack_1 <- tab_model(SI_attack_1, SI_attack_3, SI_attack_5, show.intercept = F, show.se = T, digits = 5)
comb_SI_attack_1
```

## 4.1.3. Asthma composite
```{r}
# SI_comp_0 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_composite_ever", 
#                               variables = "(1 | site_id_l_br/rel_family_id)"), 
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# SI_comp_1 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_composite_ever", variables = var_mod_1), 
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# SI_comp_2 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_composite_ever", variables = var_mod_2), 
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# SI_comp_3 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_composite_ever", variables = var_mod_3), 
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# SI_comp_4 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_composite_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# SI_comp_5 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_composite_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
#                    family = binomial, data = data_wide, nAGQ = 0)
# 
# comb_SI_comp_1 <- tab_model(SI_comp_0, SI_comp_1, SI_comp_2, SI_comp_3, SI_comp_4, SI_comp_5, show.intercept = F)
# comb_SI_comp_1
```

## 4.1.4. Recently active asthma
```{r}
# SI_recent_active_0 <- glmer(get_models(outcome = "SI_y_ever", predictor = "recent_active_asthma_ever", 
#                                        variables = "(1 | site_id_l_br/rel_family_id)"), 
#                             family = binomial, data = data_wide, nAGQ = 0)
# 
# SI_recent_active_1 <- glmer(get_models(outcome = "SI_y_ever", predictor = "recent_active_asthma_ever", variables = var_mod_1), 
#                             family = binomial, data = data_wide, nAGQ = 0)
# 
# SI_recent_active_2 <- glmer(get_models(outcome = "SI_y_ever", predictor = "recent_active_asthma_ever", variables = var_mod_2), 
#                             family = binomial, data = data_wide, nAGQ = 0)
# 
# SI_recent_active_3 <- glmer(get_models(outcome = "SI_y_ever", predictor = "recent_active_asthma_ever", variables = var_mod_3), 
#                             family = binomial, data = data_wide, nAGQ = 0)
# 
# SI_recent_active_4 <- glmer(get_models(outcome = "SI_y_ever", predictor = "recent_active_asthma_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
#                             family = binomial, data = data_wide, nAGQ = 0)
# 
# SI_recent_active_5 <- glmer(get_models(outcome = "SI_y_ever", predictor = "recent_active_asthma_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
#                             family = binomial, data = data_wide, nAGQ = 0)
# 
# comb_SI_recent_active_1 <- tab_model(SI_recent_active_0, SI_recent_active_1, SI_recent_active_2, SI_recent_active_3, SI_recent_active_4, SI_recent_active_5, show.intercept = F)
# comb_SI_recent_active_1
```

## 4.1.5. Total number of asthma attacks/Mean number of mediation and SA #asthma_num_attack_sum #Asthma_medications_2w_total_sum
```{r}
Noattack_mean_SI_wholepop_1 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_num_attack_sum",
                                         variables = "(1 | site_id_l_br/rel_family_id)"), 
                              family = binomial, data = data_wide, nAGQ = 0)

Noattack_mean_SI_wholepop_2 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_num_attack_sum",
                                         variables = var_mod_1), 
                              family = binomial, data = data_wide, nAGQ = 0)

Nomedication_mean_SI_wholepop_1 <- glmer(get_models(outcome = "SI_y_ever", predictor = "Asthma_medications_2w_total_sum",
                                             variables = "(1 | site_id_l_br/rel_family_id)"), 
                                  family = binomial, data = data_wide, nAGQ = 0)

Nomedication_mean_SI_wholepop_2 <- glmer(get_models(outcome = "SI_y_ever", predictor = "Asthma_medications_2w_total_sum",
                                             variables = var_mod_1), 
                                  family = binomial, data = data_wide, nAGQ = 0)

tab_model(Noattack_mean_SI_wholepop_1, Noattack_mean_SI_wholepop_2, Nomedication_mean_SI_wholepop_1, Nomedication_mean_SI_wholepop_2, show.intercept = F)
```

# 5. Medication - asthma
```{r}
# diagnosis
diag_med_0 <- lmer(get_models(outcome = "Asthma_medications_2w_total_sum", predictor = "asthma_diagnosis_l_ever",  #Asthma_medications_2w_total_mean
                               variables = "(1 | site_id_l_br/rel_family_id)"), data = data_wide)

diag_med_1 <- lmer(get_models(outcome = "Asthma_medications_2w_total_sum", predictor = "asthma_diagnosis_l_ever", 
                               variables = var_mod_1), data = data_wide)

tab_model(diag_med_0, diag_med_1, show.intercept = F)


# attack
attack_med_0 <- lmer(get_models(outcome = "Asthma_medications_2w_total_sum", predictor = "asthma_attack_l_ever", 
                                 variables = "(1 | site_id_l_br/rel_family_id)"), data = data_wide)

attack_med_1 <- lmer(get_models(outcome = "Asthma_medications_2w_total_sum", predictor = "asthma_attack_l_ever", 
                                 variables = var_mod_1), data = data_wide)

tab_model(attack_med_0, attack_med_1, show.intercept = F)


# composite # include medication # no models


# recent active asthma
recent_active_med_0 <- lmer(get_models(outcome = "Asthma_medications_2w_total_sum", predictor = "recent_active_asthma_ever", 
                                        variables = "(1 | site_id_l_br/rel_family_id)"), data = data_wide)

recent_active_med_1 <- lmer(get_models(outcome = "Asthma_medications_2w_total_sum", predictor = "recent_active_asthma_ever", 
                                        variables = var_mod_1), data = data_wide)

tab_model(recent_active_med_0, recent_active_med_1, show.intercept = F)
```

```{r}
# diagnosis
diag_med_0 <- glmer(get_models(outcome = "asthma_diagnosis_l_ever", predictor = "Asthma_medications_2w_total_mean",  #Asthma_medications_2w_total_mean
                              variables = "(1 | site_id_l_br/rel_family_id)"), data = data_wide, family = binomial, nAGQ = 0)

diag_med_1 <- glmer(get_models(outcome = "asthma_diagnosis_l_ever", predictor = "Asthma_medications_2w_total_mean", 
                              variables = var_mod_1), data = data_wide, family = binomial, nAGQ = 0)

tab_model(diag_med_0, diag_med_1, show.intercept = F)


# attack
attack_med_0 <- glmer(get_models(outcome = "asthma_attack_l_ever", predictor = "Asthma_medications_2w_total_mean", 
                                variables = "(1 | site_id_l_br/rel_family_id)"), data = data_wide, family = binomial)

attack_med_1 <- glmer(get_models(outcome = "asthma_attack_l_ever", predictor = "Asthma_medications_2w_total_mean", 
                                variables = var_mod_1), data = data_wide, family = binomial)

tab_model(attack_med_0, attack_med_1, show.intercept = F)


# composite # include medication # no models


# recent active asthma
recent_active_med_0 <- glmer(get_models(outcome = "recent_active_asthma_ever", predictor = "Asthma_medications_2w_total_mean", 
                                       variables = "(1 | site_id_l_br/rel_family_id)"), data = data_wide, family = binomial)

recent_active_med_1 <- glmer(get_models(outcome = "recent_active_asthma_ever", predictor = "Asthma_medications_2w_total_mean", 
                                       variables = var_mod_1), data = data_wide, family = binomial)

tab_model(recent_active_med_0, recent_active_med_1, show.intercept = F)
```

# 6. Broken bones
```{r}
brokenbones_SI_0 <- glmer(get_models(outcome = "SI_y_ever", predictor = "medhx_6a_l_ever",
                                         variables = "(1 | site_id_l_br/rel_family_id)"), 
                              family = binomial, data = data_wide, nAGQ = 0)

brokenbones_SI_1 <- glmer(get_models(outcome = "SI_y_ever", predictor = "medhx_6a_l_ever",
                                         variables = var_mod_1), 
                              family = binomial, data = data_wide, nAGQ = 0)

brokenbones_SA_0 <- glmer(get_models(outcome = "SA_y_ever", predictor = "medhx_6a_l_ever",
                                         variables = "(1 | site_id_l_br/rel_family_id)"), 
                              family = binomial, data = data_wide, nAGQ = 0)

brokenbones_SA_1 <- glmer(get_models(outcome = "SA_y_ever", predictor = "medhx_6a_l_ever",
                                         variables = var_mod_1), 
                              family = binomial, data = data_wide, nAGQ = 0)

tab_model(brokenbones_SI_0, brokenbones_SI_1)
tab_model(brokenbones_SA_0, brokenbones_SA_1)
```

# 7. Covary for medications
## 7.1. Outcome suicide ideation - asthma
### 7.1.1. Asthma diagnosis - Systemic_steroids_class_H02_2w_ever
```{r}
SI_diag_0 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", 
                              variables = "(1 | site_id_l_br/rel_family_id)"), 
                   family = binomial, data = data_wide, nAGQ = 0)

SI_diag_1 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_1), 
                   family = binomial, data = data_wide, nAGQ = 0)

SI_diag_2 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_2), 
                   family = binomial, data = data_wide, nAGQ = 0)

SI_diag_3 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3), 
                   family = binomial, data = data_wide, nAGQ = 0)

SI_diag_4 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
                   family = binomial, data = data_wide, nAGQ = 0)

SI_diag_5 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                   family = binomial, data = data_wide, nAGQ = 0)

SI_diag_02 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", 
                               variables = c("(1 | site_id_l_br/rel_family_id)", "Systemic_steroids_class_H02_2w_ever")), 
                    family = binomial, data = data_wide, nAGQ = 0)

SI_diag_12 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", 
                               variables = var_mod_1, var_added = "Systemic_steroids_class_H02_2w_ever"),
                    family = binomial, data = data_wide, nAGQ = 0)

SI_diag_32 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", 
                               variables = var_mod_3, var_added = "Systemic_steroids_class_H02_2w_ever"),
                    family = binomial, data = data_wide, nAGQ = 0)

SI_diag_52 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, 
                               var_added = c("scale(BPM_mean)", "Systemic_steroids_class_H02_2w_ever")),
                    family = binomial, data = data_wide, nAGQ = 0)

# comb_SI_diag_1 <- tab_model(SI_diag_1, SI_diag_3, SI_diag_5, show.intercept = F, show.se = T, digits = 5)
# comb_SI_diag_1 <- 
#   tab_model(SI_diag_02, SI_diag_1, SI_diag_12, SI_diag_3, SI_diag_32, SI_diag_5, SI_diag_52, show.intercept = F, show.se = T, digits = 5)

comb_SI_diag_1 <- 
  tab_model(SI_diag_12, SI_diag_32, SI_diag_52, show.intercept = F, show.se = T, digits = 5)
comb_SI_diag_1
```

## 4.1.2. Asthma attack - Systemic_steroids_class_H02_2w_ever
```{r}
SI_attack_steroid_0 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", 
                                variables = "(1 | site_id_l_br/rel_family_id)"), 
                     family = binomial, data = data_wide, nAGQ = 0)

SI_attack_steroid_1 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_1), 
                     family = binomial, data = data_wide, nAGQ = 0)

SI_attack_steroid_2 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_2), 
                     family = binomial, data = data_wide, nAGQ = 0)

SI_attack_steroid_3 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3), 
                     family = binomial, data = data_wide, nAGQ = 0)

SI_attack_steroid_4 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
                     family = binomial, data = data_wide, nAGQ = 0)

SI_attack_steroid_5 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                     family = binomial, data = data_wide, nAGQ = 0)

SI_attack_steroid_02 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", 
                                 variables = c("(1 | site_id_l_br/rel_family_id)", "Systemic_steroids_class_H02_2w_ever")), 
                      family = binomial, data = data_wide, nAGQ = 0)

SI_attack_steroid_12 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", 
                                 variables = var_mod_1, var_added = "Systemic_steroids_class_H02_2w_ever"),
                      family = binomial, data = data_wide, nAGQ = 0)

SI_attack_steroid_32 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", 
                                 variables = var_mod_3, var_added = "Systemic_steroids_class_H02_2w_ever"),
                      family = binomial, data = data_wide, nAGQ = 0)

SI_attack_steroid_52 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, 
                                 var_added = c("scale(BPM_mean)", "Systemic_steroids_class_H02_2w_ever")),
                      family = binomial, data = data_wide, nAGQ = 0)

# comb_SI_attack_steroid_1 <- tab_model(SI_attack_steroid_0, SI_attack_steroid_1, SI_attack_steroid_2, SI_attack_steroid_3, SI_attack_steroid_4, SI_attack_steroid_5, show.intercept = F)
# comb_SI_attack_steroid_1 <- 
#   tab_model(SI_attack_steroid_02, SI_attack_steroid_1, SI_attack_steroid_12, SI_attack_steroid_3, SI_attack_steroid_32, SI_attack_steroid_5, SI_attack_steroid_52, show.intercept = F, show.se = T, digits = 5)

comb_SI_attack_steroid_1 <- 
  tab_model(SI_attack_steroid_12, SI_attack_steroid_32, SI_attack_steroid_52, show.intercept = F, show.se = T, digits = 5)
comb_SI_attack_steroid_1
```

# All meds listed as either SSRI or Other_antidepressants_anxiety
```{r}
data_wide <- 
  create_ever_var(data = data_wide, search_term = "SSRI_2w_ever|Other_antidepressants_anxiety_2w_ever", new_col_name = "SSRI_antidepress")

data_wide <- 
  create_ever_var(data = data_wide, 
                  search_term = "SSRI_2w_ever|Other_antidepressants_anxiety_2w_ever|Asthma_medications_2w_ever", 
                  new_col_name = "SSRI_antidepress_asthmamed")


# data_wide$SSRI_antidepress <- apply(data_wide[,grepl("SSRI_2w_ever|Other_antidepressants_anxiety_2w_ever", colnames(data_wide))],1 ,function(x) {any(x == 1)*1})
# data_wide$SSRI_antidepress <- ifelse( (is.na(data_wide$SSRI_antidepress) &
#                                                      (apply(data_wide[,which(grepl("SSRI_2w_ever|Other_antidepressants_anxiety_2w_ever", colnames(data_wide)))], 1, function(x) {any(x == 0)}))),
#                                                   0, data_wide$SSRI_antidepress)
```

```{r}
SI_diag_SSRI_antidepress_0 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                                 variables = "(1 | site_id_l_br/rel_family_id)"), 
                                      family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_1 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_1), 
                                      family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_2 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_2), 
                                      family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_3 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3), 
                                      family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_4 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
                                      family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_5 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                                      family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_02 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                                  variables = c("(1 | site_id_l_br/rel_family_id)", "SSRI_antidepress")), 
                                       family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_12 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                                  variables = var_mod_1, var_added = "SSRI_antidepress"),
                                       family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_32 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                                  variables = var_mod_3, var_added = "SSRI_antidepress"),
                                       family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_52 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, 
                                                  var_added = c("scale(BPM_mean)", "SSRI_antidepress")),
                                       family = binomial, data = data_wide, nAGQ = 0)

# comb_SI_diag_SSRI_antidepress_1 <- tab_model(SI_diag_SSRI_antidepress_0, SI_diag_SSRI_antidepress_1, SI_diag_SSRI_antidepress_2, SI_diag_SSRI_antidepress_3, SI_diag_SSRI_antidepress_4, SI_diag_SSRI_antidepress_5, show.intercept = F)
# comb_SI_diag_SSRI_antidepress_1 <- 
#   tab_model(SI_diag_SSRI_antidepress_02, SI_diag_SSRI_antidepress_1, SI_diag_SSRI_antidepress_12, SI_diag_SSRI_antidepress_3, SI_diag_SSRI_antidepress_32, SI_diag_SSRI_antidepress_5, SI_diag_SSRI_antidepress_52, show.intercept = F, show.se = T, digits = 5)

comb_SI_diag_SSRI_antidepress_1 <- 
  tab_model(SI_diag_SSRI_antidepress_12, SI_diag_SSRI_antidepress_32, SI_diag_SSRI_antidepress_52, show.intercept = F, show.se = T, digits = 5)

comb_SI_diag_SSRI_antidepress_1
```

## 4.1.2. Asthma attack - SSRI_antidepress
```{r}
SI_attack_SSRI_antidepress_0 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", 
                                variables = "(1 | site_id_l_br/rel_family_id)"), 
                     family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_1 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_1), 
                     family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_2 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_2), 
                     family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_3 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3), 
                     family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_4 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
                     family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_5 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                     family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_02 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", 
                                 variables = c("(1 | site_id_l_br/rel_family_id)", "SSRI_antidepress")), 
                      family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_12 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", 
                                 variables = var_mod_1, var_added = "SSRI_antidepress"),
                      family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_32 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", 
                                 variables = var_mod_3, var_added = "SSRI_antidepress"),
                      family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_52 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, 
                                 var_added = c("scale(BPM_mean)", "SSRI_antidepress")),
                      family = binomial, data = data_wide, nAGQ = 0)

# comb_SI_attack_SSRI_antidepress_1 <- tab_model(SI_attack_SSRI_antidepress_0, SI_attack_SSRI_antidepress_1, SI_attack_SSRI_antidepress_2, SI_attack_SSRI_antidepress_3, SI_attack_SSRI_antidepress_4, SI_attack_SSRI_antidepress_5, show.intercept = F)
# comb_SI_attack_SSRI_antidepress_1 <- 
#   tab_model(SI_attack_SSRI_antidepress_02, SI_attack_SSRI_antidepress_1, SI_attack_SSRI_antidepress_12, SI_attack_SSRI_antidepress_3, SI_attack_SSRI_antidepress_32, SI_attack_SSRI_antidepress_5, SI_attack_SSRI_antidepress_52, show.intercept = F, show.se = T, digits = 5)

comb_SI_attack_SSRI_antidepress_1 <- 
  tab_model(SI_attack_SSRI_antidepress_12, SI_attack_SSRI_antidepress_32, SI_attack_SSRI_antidepress_52, show.intercept = F, show.se = T, digits = 5)

comb_SI_attack_SSRI_antidepress_1
```



```{r}
SI_diag_SSRI_antidepress_asthmamed_0 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                               variables = "(1 | site_id_l_br/rel_family_id)"), 
                                    family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_asthmamed_1 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_1), 
                                    family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_asthmamed_2 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_2), 
                                    family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_asthmamed_3 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3), 
                                    family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_asthmamed_4 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
                                    family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_asthmamed_5 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                                    family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_asthmamed_02 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                                variables = c("(1 | site_id_l_br/rel_family_id)", "SSRI_antidepress_asthmamed")), 
                                     family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_asthmamed_12 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                                variables = var_mod_1, var_added = "SSRI_antidepress_asthmamed"),
                                     family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_asthmamed_32 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                                variables = var_mod_3, var_added = "SSRI_antidepress_asthmamed"),
                                     family = binomial, data = data_wide, nAGQ = 0)

SI_diag_SSRI_antidepress_asthmamed_52 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, 
                                                var_added = c("scale(BPM_mean)", "SSRI_antidepress_asthmamed")),
                                     family = binomial, data = data_wide, nAGQ = 0)

# comb_SI_diag_SSRI_antidepress_asthmamed_1 <- tab_model(SI_diag_SSRI_antidepress_asthmamed_0, SI_diag_SSRI_antidepress_asthmamed_1, SI_diag_SSRI_antidepress_asthmamed_2, SI_diag_SSRI_antidepress_asthmamed_3, SI_diag_SSRI_antidepress_asthmamed_4, SI_diag_SSRI_antidepress_asthmamed_5, show.intercept = F)
# comb_SI_diag_SSRI_antidepress_asthmamed_1 <- 
#   tab_model(SI_diag_SSRI_antidepress_asthmamed_02, SI_diag_SSRI_antidepress_asthmamed_1, SI_diag_SSRI_antidepress_asthmamed_12, SI_diag_SSRI_antidepress_asthmamed_3, SI_diag_SSRI_antidepress_asthmamed_32, SI_diag_SSRI_antidepress_asthmamed_5, SI_diag_SSRI_antidepress_asthmamed_52, show.intercept = F, show.se = T, digits = 5)

comb_SI_diag_SSRI_antidepress_asthmamed_1 <- 
  tab_model(SI_diag_SSRI_antidepress_asthmamed_12, SI_diag_SSRI_antidepress_asthmamed_32, SI_diag_SSRI_antidepress_asthmamed_52, show.intercept = F, show.se = T, digits = 5)


comb_SI_diag_SSRI_antidepress_asthmamed_1
```

## 4.1.2. Asthma attack - SSRI_antidepress
```{r}
SI_attack_SSRI_antidepress_asthmamed_0 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", 
                                                 variables = "(1 | site_id_l_br/rel_family_id)"), 
                                      family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_asthmamed_1 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_1), 
                                      family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_asthmamed_2 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_2), 
                                      family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_asthmamed_3 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3), 
                                      family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_asthmamed_4 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
                                      family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_asthmamed_5 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                                      family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_asthmamed_02 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", 
                                                  variables = c("(1 | site_id_l_br/rel_family_id)", "SSRI_antidepress_asthmamed")), 
                                       family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_asthmamed_12 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", 
                                                  variables = var_mod_1, var_added = "SSRI_antidepress_asthmamed"),
                                       family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_asthmamed_32 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", 
                                                  variables = var_mod_3, var_added = "SSRI_antidepress_asthmamed"),
                                       family = binomial, data = data_wide, nAGQ = 0)

SI_attack_SSRI_antidepress_asthmamed_52 <- glmer(get_models(outcome = "SI_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, 
                                                  var_added = c("scale(BPM_mean)", "SSRI_antidepress_asthmamed")),
                                       family = binomial, data = data_wide, nAGQ = 0)

# comb_SI_attack_SSRI_antidepress_asthmamed_1 <- tab_model(SI_attack_SSRI_antidepress_asthmamed_0, SI_attack_SSRI_antidepress_asthmamed_1, SI_attack_SSRI_antidepress_asthmamed_2, SI_attack_SSRI_antidepress_asthmamed_3, SI_attack_SSRI_antidepress_asthmamed_4, SI_attack_SSRI_antidepress_asthmamed_5, show.intercept = F)
# comb_SI_attack_SSRI_antidepress_asthmamed_1 <- 
#   tab_model(SI_attack_SSRI_antidepress_asthmamed_02, SI_attack_SSRI_antidepress_asthmamed_1, SI_attack_SSRI_antidepress_asthmamed_12, SI_attack_SSRI_antidepress_asthmamed_3, SI_attack_SSRI_antidepress_asthmamed_32, SI_attack_SSRI_antidepress_asthmamed_5, SI_attack_SSRI_antidepress_asthmamed_52, show.intercept = F, show.se = T, digits = 5)

comb_SI_attack_SSRI_antidepress_asthmamed_1 <- 
  tab_model(SI_attack_SSRI_antidepress_asthmamed_12, SI_attack_SSRI_antidepress_asthmamed_32, SI_attack_SSRI_antidepress_asthmamed_52, show.intercept = F, show.se = T, digits = 5)

comb_SI_attack_SSRI_antidepress_asthmamed_1
```

## 7.1. Outcome suicide attempt - asthma
### 7.1.1. Asthma diagnosis - Systemic_steroids_class_H02_2w_ever
```{r}
SA_diag_0 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", 
                              variables = "(1 | site_id_l_br/rel_family_id)"), 
                   family = binomial, data = data_wide, nAGQ = 0)

SA_diag_1 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_1), 
                   family = binomial, data = data_wide, nAGQ = 0)

SA_diag_2 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_2), 
                   family = binomial, data = data_wide, nAGQ = 0)

SA_diag_3 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3), 
                   family = binomial, data = data_wide, nAGQ = 0)

SA_diag_4 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
                   family = binomial, data = data_wide, nAGQ = 0)

SA_diag_5 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                   family = binomial, data = data_wide, nAGQ = 0)

SA_diag_02 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", 
                               variables = c("(1 | site_id_l_br/rel_family_id)", "Systemic_steroids_class_H02_2w_ever")), 
                    family = binomial, data = data_wide, nAGQ = 0)

SA_diag_12 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", 
                               variables = var_mod_1, var_added = "Systemic_steroids_class_H02_2w_ever"),
                    family = binomial, data = data_wide, nAGQ = 0)

SA_diag_32 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", 
                               variables = var_mod_3, var_added = "Systemic_steroids_class_H02_2w_ever"),
                    family = binomial, data = data_wide, nAGQ = 0)

SA_diag_52 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, 
                               var_added = c("scale(BPM_mean)", "Systemic_steroids_class_H02_2w_ever")),
                    family = binomial, data = data_wide, nAGQ = 0)

# comb_SA_diag_1 <- tab_model(SA_diag_1, SA_diag_3, SA_diag_5, show.intercept = F, show.se = T, digits = 5)
comb_SA_diag_1 <- 
  tab_model(SA_diag_12, SA_diag_32, SA_diag_52, show.intercept = F, show.se = T, digits = 5)
comb_SA_diag_1
```

## 4.1.2. Asthma attack - Systemic_steroids_class_H02_2w_ever
```{r}
SA_attack_steroid_0 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", 
                                        variables = "(1 | site_id_l_br/rel_family_id)"), 
                             family = binomial, data = data_wide, nAGQ = 0)

SA_attack_steroid_1 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_1), 
                             family = binomial, data = data_wide, nAGQ = 0)

SA_attack_steroid_2 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_2), 
                             family = binomial, data = data_wide, nAGQ = 0)

SA_attack_steroid_3 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3), 
                             family = binomial, data = data_wide, nAGQ = 0)

SA_attack_steroid_4 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
                             family = binomial, data = data_wide, nAGQ = 0)

SA_attack_steroid_5 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                             family = binomial, data = data_wide, nAGQ = 0)

SA_attack_steroid_02 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", 
                                         variables = c("(1 | site_id_l_br/rel_family_id)", "Systemic_steroids_class_H02_2w_ever")), 
                              family = binomial, data = data_wide, nAGQ = 0)

SA_attack_steroid_12 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", 
                                         variables = var_mod_1, var_added = "Systemic_steroids_class_H02_2w_ever"),
                              family = binomial, data = data_wide, nAGQ = 0)

SA_attack_steroid_32 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", 
                                         variables = var_mod_3, var_added = "Systemic_steroids_class_H02_2w_ever"),
                              family = binomial, data = data_wide, nAGQ = 0)

SA_attack_steroid_52 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, 
                                         var_added = c("scale(BPM_mean)", "Systemic_steroids_class_H02_2w_ever")),
                              family = binomial, data = data_wide, nAGQ = 0)

# comb_SA_attack_steroid_1 <- tab_model(SA_attack_steroid_0, SA_attack_steroid_1, SA_attack_steroid_2, SA_attack_steroid_3, SA_attack_steroid_4, SA_attack_steroid_5, show.intercept = F)
comb_SA_attack_steroid_1 <- 
  tab_model(SA_attack_steroid_12, SA_attack_steroid_32, SA_attack_steroid_52, show.intercept = F, show.se = T, digits = 5)
comb_SA_attack_steroid_1
```


```{r}
SA_diag_SSRI_antidepress_0 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                               variables = "(1 | site_id_l_br/rel_family_id)"), 
                                    family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_1 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_1), 
                                    family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_2 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_2), 
                                    family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_3 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3), 
                                    family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_4 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
                                    family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_5 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                                    family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_02 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                                variables = c("(1 | site_id_l_br/rel_family_id)", "SSRI_antidepress")), 
                                     family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_12 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                                variables = var_mod_1, var_added = "SSRI_antidepress"),
                                     family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_32 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                                variables = var_mod_3, var_added = "SSRI_antidepress"),
                                     family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_52 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, 
                                                var_added = c("scale(BPM_mean)", "SSRI_antidepress")),
                                     family = binomial, data = data_wide, nAGQ = 0)

# comb_SA_diag_SSRI_antidepress_1 <- tab_model(SA_diag_SSRI_antidepress_0, SA_diag_SSRI_antidepress_1, SA_diag_SSRI_antidepress_2, SA_diag_SSRI_antidepress_3, SA_diag_SSRI_antidepress_4, SA_diag_SSRI_antidepress_5, show.intercept = F)
comb_SA_diag_SSRI_antidepress_1 <- 
  tab_model(SA_diag_SSRI_antidepress_12, SA_diag_SSRI_antidepress_32, SA_diag_SSRI_antidepress_52, show.intercept = F, show.se = T, digits = 5)
comb_SA_diag_SSRI_antidepress_1
```

## 4.1.2. Asthma attack - SSRI_antidepress
```{r}
SA_attack_SSRI_antidepress_0 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", 
                                                 variables = "(1 | site_id_l_br/rel_family_id)"), 
                                      family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_1 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_1), 
                                      family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_2 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_2), 
                                      family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_3 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3), 
                                      family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_4 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
                                      family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_5 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                                      family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_02 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", 
                                                  variables = c("(1 | site_id_l_br/rel_family_id)", "SSRI_antidepress")), 
                                       family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_12 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", 
                                                  variables = var_mod_1, var_added = "SSRI_antidepress"),
                                       family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_32 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", 
                                                  variables = var_mod_3, var_added = "SSRI_antidepress"),
                                       family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_52 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, 
                                                  var_added = c("scale(BPM_mean)", "SSRI_antidepress")),
                                       family = binomial, data = data_wide, nAGQ = 0)

# comb_SA_attack_SSRI_antidepress_1 <- tab_model(SA_attack_SSRI_antidepress_0, SA_attack_SSRI_antidepress_1, SA_attack_SSRI_antidepress_2, SA_attack_SSRI_antidepress_3, SA_attack_SSRI_antidepress_4, SA_attack_SSRI_antidepress_5, show.intercept = F)
comb_SA_attack_SSRI_antidepress_1 <- 
  tab_model(SA_attack_SSRI_antidepress_12, SA_attack_SSRI_antidepress_32, SA_attack_SSRI_antidepress_52, show.intercept = F, show.se = T, digits = 5)
comb_SA_attack_SSRI_antidepress_1
```



```{r}
SA_diag_SSRI_antidepress_asthmamed_0 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                                         variables = "(1 | site_id_l_br/rel_family_id)"), 
                                              family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_asthmamed_1 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_1), 
                                              family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_asthmamed_2 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_2), 
                                              family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_asthmamed_3 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3), 
                                              family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_asthmamed_4 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
                                              family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_asthmamed_5 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                                              family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_asthmamed_02 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                                          variables = c("(1 | site_id_l_br/rel_family_id)", "SSRI_antidepress_asthmamed")), 
                                               family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_asthmamed_12 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                                          variables = var_mod_1, var_added = "SSRI_antidepress_asthmamed"),
                                               family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_asthmamed_32 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", 
                                                          variables = var_mod_3, var_added = "SSRI_antidepress_asthmamed"),
                                               family = binomial, data = data_wide, nAGQ = 0)

SA_diag_SSRI_antidepress_asthmamed_52 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_diagnosis_l_ever", variables = var_mod_3, 
                                                          var_added = c("scale(BPM_mean)", "SSRI_antidepress_asthmamed")),
                                               family = binomial, data = data_wide, nAGQ = 0)

# comb_SA_diag_SSRI_antidepress_asthmamed_1 <- tab_model(SA_diag_SSRI_antidepress_asthmamed_0, SA_diag_SSRI_antidepress_asthmamed_1, SA_diag_SSRI_antidepress_asthmamed_2, SA_diag_SSRI_antidepress_asthmamed_3, SA_diag_SSRI_antidepress_asthmamed_4, SA_diag_SSRI_antidepress_asthmamed_5, show.intercept = F)
comb_SA_diag_SSRI_antidepress_asthmamed_1 <- 
  tab_model(SA_diag_SSRI_antidepress_asthmamed_12, SA_diag_SSRI_antidepress_asthmamed_32, SA_diag_SSRI_antidepress_asthmamed_52, show.intercept = F, show.se = T, digits = 5)
comb_SA_diag_SSRI_antidepress_asthmamed_1
```

## 4.1.2. Asthma attack - SSRI_antidepress
```{r}
SA_attack_SSRI_antidepress_asthmamed_0 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", 
                                                           variables = "(1 | site_id_l_br/rel_family_id)"), 
                                                family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_asthmamed_1 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_1), 
                                                family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_asthmamed_2 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_2), 
                                                family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_asthmamed_3 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3), 
                                                family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_asthmamed_4 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(CBCL_mean)"),
                                                family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_asthmamed_5 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, var_added = "scale(BPM_mean)"),
                                                family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_asthmamed_02 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", 
                                                            variables = c("(1 | site_id_l_br/rel_family_id)", "SSRI_antidepress_asthmamed")), 
                                                 family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_asthmamed_12 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", 
                                                            variables = var_mod_1, var_added = "SSRI_antidepress_asthmamed"),
                                                 family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_asthmamed_32 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", 
                                                            variables = var_mod_3, var_added = "SSRI_antidepress_asthmamed"),
                                                 family = binomial, data = data_wide, nAGQ = 0)

SA_attack_SSRI_antidepress_asthmamed_52 <- glmer(get_models(outcome = "SA_y_ever", predictor = "asthma_attack_l_ever", variables = var_mod_3, 
                                                            var_added = c("scale(BPM_mean)", "SSRI_antidepress_asthmamed")),
                                                 family = binomial, data = data_wide, nAGQ = 0)

# comb_SA_attack_SSRI_antidepress_asthmamed_1 <- tab_model(SA_attack_SSRI_antidepress_asthmamed_0, SA_attack_SSRI_antidepress_asthmamed_1, SA_attack_SSRI_antidepress_asthmamed_2, SA_attack_SSRI_antidepress_asthmamed_3, SA_attack_SSRI_antidepress_asthmamed_4, SA_attack_SSRI_antidepress_asthmamed_5, show.intercept = F)
comb_SA_attack_SSRI_antidepress_asthmamed_1 <- 
  tab_model(SA_attack_SSRI_antidepress_asthmamed_12, SA_attack_SSRI_antidepress_asthmamed_32, SA_attack_SSRI_antidepress_asthmamed_52, show.intercept = F, show.se = T, digits = 5)
comb_SA_attack_SSRI_antidepress_asthmamed_1
```






