---
title: "Mixed models"
author: "Kate Tran"
date: "7/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(readr)
library(lme4)
library(sjPlot)
library(gtsummary)
```

# 1. Read data 

```{r}
dataset <- "../outputs/asthma_inflammation_set.csv" %>% read_csv()

dataset <- dataset %>%
  dplyr::mutate(age_years = interview_age/12) %>% 
  dplyr::mutate(across(
  c(src_subject_id, rel_family_id, site_id_l_br), as.factor)) %>%
  dplyr::mutate(across(
    c(
      sex_br,
      race_white,
      race_black,
      race_asian,
      ethnicity_hisp,
      asthma_diagnosis_l,
      asthma_attack_l,
      asthma_composite,
      Asthma_medications_2w,
      recent_active_asthma,
      suicidality_y,
      SA_y,
      SI_y,
      medhx_6a_l
    ),
    ~ factor(., levels = c("0", "1"))
  )) %>%
  dplyr::mutate(across(
  c(household_income, timepoint, asthma_PRS), as.numeric))

with(dataset, table(SA_y, eventname))
```

# 2. Check association between asthma diagnosis and CBCL
```{r}
diag_cbcl <- lmer(scale(cbcl_scr_syn_totprob_r) ~ asthma_diagnosis_l + (1 | site_id_l_br/rel_family_id/src_subject_id),
      data = dataset,
     control=lmerControl(check.nobs.vs.nlev = "ignore",
                                      check.nobs.vs.rankZ = "ignore",
                                      check.nobs.vs.nRE="ignore",
                                      optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))
tab_model(diag_cbcl)
```

# 3. Models' formula
```{r}
# Outcome: suicidality_y
var_mod_1 <- c(
  # "timepoint", #fixed-effect model matrix is rank deficient so dropping 1 column / coefficient
  "scale(age_years)",
  "sex_br",
  "race_white",
  "race_black",
  "race_other",
  "ethnicity_hisp",
  "(1 | site_id_l_br/rel_family_id/src_subject_id)"
)

var_mod_2 <- c(
  var_mod_1,
  "scale(household_income)",
  "scale(parents_avg_edu)",
  "scale(devhx_3_p)"
)

var_mod_3 <- c(
  var_mod_2,
  "reshist_addr1_adi_perc",
  "scale(reshist_addr1_popdensity)",
  "scale(reshist_addr1_no2)",
  "scale(reshist_addr1_pm25)",
  "scale(reshist_addr1_proxrd)"
)

models <- function(outcome, predictor, variables, var_added) {
  # predictor <- paste0("scale(", predictor, ")", sep = "")
  if (is.null(var_added)) {
    model <- as.formula(paste0(outcome, " ~", paste0(c(
      predictor, variables
    ), collapse = " + "), sep = ""))
  } else {
    model <- as.formula(paste0(outcome, " ~", paste0(
      c(predictor, variables, var_added), collapse = " + "
    ), sep = ""))
  }
  return(model)
}
```

# 4. SUICIDE ATTEMPT
# 4.1. Outcome suicide attempt - asthma
```{r}
SA_diag_0 <- glmer(models(outcome = "SA_y", predictor = "asthma_diagnosis_l", 
                             variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                      family = binomial, data = dataset, nAGQ = 0)

SA_diag_1 <- glmer(models(outcome = "SA_y", predictor = "asthma_diagnosis_l", variables = var_mod_1, var_added = NULL), 
                      family = binomial, data = dataset, nAGQ = 0)

SA_diag_2 <- glmer(models(outcome = "SA_y", predictor = "asthma_diagnosis_l", variables = var_mod_2, var_added = NULL), 
                      family = binomial, data = dataset, nAGQ = 0)

SA_diag_3 <- glmer(models(outcome = "SA_y", predictor = "asthma_diagnosis_l", variables = var_mod_3, var_added = NULL), 
                      family = binomial, data = dataset, nAGQ = 0)

SA_diag_4 <- glmer(models(outcome = "SA_y", predictor = "asthma_diagnosis_l", variables = var_mod_3, var_added = "scale(cbcl_scr_syn_totprob_r)"),
family = binomial, data = dataset, nAGQ = 0)

# SA_diag_4_black <- glmer(models(outcome = "SA_y", predictor = "asthma_diagnosis_l", 
#                                       variables = var_mod_3[var_mod_3 != "race_black" & var_mod_3 != "race_white"], 
#                                    var_added = "scale(asthma_PRS)"), family = binomial, data = dataset %>% filter(genetic_afr == 1),
#                             nAGQ = 0)
# 
# SA_diag_4_white <- glmer(models(outcome = "SA_y", predictor = "asthma_diagnosis_l", 
#                                       variables = var_mod_3[var_mod_3 != "race_black" & var_mod_3 != "race_white"], 
#                                    var_added = "scale(asthma_PRS)"), family = binomial, data = dataset %>% filter(genetic_afr == 0),
#                             nAGQ = 0)
# 
# SA_diag_5 <- glmer(models(outcome = "SA_y", predictor = "asthma_diagnosis_l", variables = var_mod_3, 
#                              var_added = "scale(asthma_PRS)"), family = binomial, data = dataset,
#                       nAGQ = 0)

comb_SA_diag_1 <- tab_model(SA_diag_0, SA_diag_1, SA_diag_2, SA_diag_3, SA_diag_4)
comb_SA_diag_1
```

```{r}
SA_attack_0 <- glmer(models(outcome = "SA_y", predictor = "asthma_attack_l",
                               variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL),
                        family = binomial, data = dataset, nAGQ = 0)

SA_attack_1 <- glmer(models(outcome = "SA_y", predictor = "asthma_attack_l", variables = var_mod_1, var_added = NULL),
                        family = binomial, data = dataset, nAGQ = 0)

SA_attack_2 <- glmer(models(outcome = "SA_y", predictor = "asthma_attack_l", variables = var_mod_2, var_added = NULL),
                        family = binomial, data = dataset, nAGQ = 0)

SA_attack_3 <- glmer(models(outcome = "SA_y", predictor = "asthma_attack_l", variables = var_mod_3, var_added = NULL),
                        family = binomial, data = dataset, nAGQ = 0)

SA_attack_4 <- glmer(models(outcome = "SA_y", predictor = "asthma_attack_l", variables = var_mod_3, var_added = "scale(cbcl_scr_syn_totprob_r)"),
                        family = binomial, data = dataset, nAGQ = 0)

# SA_attack_4_black <- glmer(models(outcome = "SA_y", predictor = "asthma_attack_l", 
#                                         variables = var_mod_3[var_mod_3 != "race_black" & var_mod_3 != "race_white"],
#                                      var_added = "asthma_PRS"),  family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)
# 
# SA_attack_4_white <- glmer(models(outcome = "SA_y", predictor = "asthma_attack_l", 
#                                         variables = var_mod_3[var_mod_3 != "race_black" & var_mod_3 != "race_white"],
#                                      var_added = "asthma_PRS"),  family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)
# 
# SA_attack_4 <- glmer(models(outcome = "SA_y", predictor = "asthma_attack_l", variables = var_mod_3,
#                                var_added = "asthma_PRS"),  family = binomial, data = dataset, nAGQ = 0)

comb_SA_attack_1 <- tab_model(SA_attack_0, SA_attack_1, SA_attack_2, SA_attack_3, SA_attack_4)
comb_SA_attack_1
```

```{r}
SA_comp_0 <- glmer(models(outcome = "SA_y", predictor = "asthma_composite", 
                             variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                      family = binomial, data = dataset, nAGQ = 0)

SA_comp_1 <- glmer(models(outcome = "SA_y", predictor = "asthma_composite", variables = var_mod_1, var_added = NULL), 
                      family = binomial, data = dataset, nAGQ = 0)

SA_comp_2 <- glmer(models(outcome = "SA_y", predictor = "asthma_composite", variables = var_mod_2, var_added = NULL), 
                      family = binomial, data = dataset, nAGQ = 0)

SA_comp_3 <- glmer(models(outcome = "SA_y", predictor = "asthma_composite", variables = var_mod_3, var_added = NULL), 
                      family = binomial, data = dataset, nAGQ = 0)

SA_comp_4 <- glmer(models(outcome = "SA_y", predictor = "asthma_composite", variables = var_mod_3, var_added = "scale(cbcl_scr_syn_totprob_r)"), 
                      family = binomial, data = dataset, nAGQ = 0)

# SA_comp_4_black <- glmer(models(outcome = "SA_y", predictor = "asthma_composite", 
#                                       variables = var_mod_3[var_mod_3 != "race_black" & var_mod_3 != "race_white"], 
#                                    var_added = "asthma_PRS"),  family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)
# 
# SA_comp_4_white <- glmer(models(outcome = "SA_y", predictor = "asthma_composite", 
#                                       variables = var_mod_3[var_mod_3 != "race_black" & var_mod_3 != "race_white"], 
#                                    var_added = "asthma_PRS"),  family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)
# 
# SA_comp_4 <- glmer(models(outcome = "SA_y", predictor = "asthma_composite", variables = var_mod_3, 
#                              var_added = "asthma_PRS"),  family = binomial, data = dataset, nAGQ = 0)


comb_SA_comp_1 <- tab_model(SA_comp_0, SA_comp_1, SA_comp_2, SA_comp_3, SA_comp_4)
comb_SA_comp_1
```

# 4.2. Outcome suicide attempt - genetic scores

```{r}
SA_gen_0_black <- glmer(models(outcome = "SA_y", predictor = "asthma_PRS",
                                  variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                           family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)

SA_gen_0_white <- glmer(models(outcome = "SA_y", predictor = "asthma_PRS",
                                  variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                           family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)

SA_gen_1_black <- glmer(models(outcome = "SA_y", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                           family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)

SA_gen_1_white <- glmer(models(outcome = "SA_y", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                           family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)

SA_gen_2_black <- glmer(models(outcome = "SA_y", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                           family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)

SA_gen_2_white <- glmer(models(outcome = "SA_y", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                           family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)

SA_gen_3_black <- glmer(models(outcome = "SA_y", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                           family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)

SA_gen_3_white <- glmer(models(outcome = "SA_y", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                           family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)

comb_SA_gen_1 <- tab_model(SA_gen_0_black, SA_gen_0_white, SA_gen_1_black, SA_gen_1_white, SA_gen_2_black, SA_gen_2_white, 
                        SA_gen_3_black, SA_gen_3_white)
comb_SA_gen_1
```

# 4.3. Number of asthma attack and SA #medhx_ss_6l_times_p_l
```{r}
# Among people with asthma attack only
Noattack_SA_1_1 <- glmer(models(outcome = "SA_y", predictor = "medhx_ss_6l_times_p_l",
                                  variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                           family = binomial, data = dataset %>% filter(asthma_attack_l == 1), nAGQ = 0)

Noattack_SA_1_2 <- glmer(models(outcome = "SA_y", predictor = "medhx_ss_6l_times_p_l",
                                  variables = var_mod_1, var_added = NULL), 
                           family = binomial, data = dataset %>% filter(asthma_attack_l == 1), nAGQ = 0)

Nomedication_SA_1_1 <- glmer(models(outcome = "SA_y", predictor = "Asthma_medications_2w_total",
                                  variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                           family = binomial, data = dataset %>% filter(asthma_attack_l == 1), nAGQ = 0)

Nomedication_SA_1_2 <- glmer(models(outcome = "SA_y", predictor = "Asthma_medications_2w_total",
                                  variables = var_mod_1, var_added = NULL), 
                           family = binomial, data = dataset %>% filter(asthma_attack_l == 1), nAGQ = 0)

tab_model(Noattack_SA_1_1, Noattack_SA_1_2, Nomedication_SA_1_1, Nomedication_SA_1_2)

# Among people with asthma diagnosis only
Noattack_SA_2_1 <- glmer(models(outcome = "SA_y", predictor = "medhx_ss_6l_times_p_l",
                                  variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                           family = binomial, data = dataset %>% filter(asthma_diagnosis_l == 1), nAGQ = 0)

Noattack_SA_2_2 <- glmer(models(outcome = "SA_y", predictor = "medhx_ss_6l_times_p_l",
                                  variables = var_mod_1, var_added = NULL), 
                           family = binomial, data = dataset %>% filter(asthma_diagnosis_l == 1), nAGQ = 0)

Nomedication_SA_2_1 <- glmer(models(outcome = "SA_y", predictor = "Asthma_medications_2w_total",
                                  variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                           family = binomial, data = dataset %>% filter(asthma_diagnosis_l == 1), nAGQ = 0)

Nomedication_SA_2_2 <- glmer(models(outcome = "SA_y", predictor = "Asthma_medications_2w_total",
                                  variables = var_mod_1, var_added = NULL), 
                           family = binomial, data = dataset %>% filter(asthma_diagnosis_l == 1), nAGQ = 0)

tab_model(Noattack_SA_2_1, Noattack_SA_2_2, Nomedication_SA_2_1, Nomedication_SA_2_2)

# remove 0 asthma attack (for mod1)
Noattack_SA_3_1 <- glmer(models(outcome = "SA_y", predictor = "medhx_ss_6l_times_p_l",
                                  variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                           family = binomial, data = dataset %>% filter(medhx_ss_6a_times_p_l > 0), nAGQ = 0)

Noattack_SA_3_2 <- glmer(models(outcome = "SA_y", predictor = "medhx_ss_6l_times_p_l",
                                  variables = var_mod_1, var_added = NULL), 
                           family = binomial, data = dataset %>% filter(medhx_ss_6a_times_p_l > 0), nAGQ = 0)

tab_model(Noattack_SA_3_1, Noattack_SA_3_2)

# remove 0 medications (for mod2)
Nomedication_SA_3_1 <- glmer(models(outcome = "SA_y", predictor = "Asthma_medications_2w_total",
                                  variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                           family = binomial, data = dataset %>% filter(Asthma_medications_2w_total > 0), nAGQ = 0)

Nomedication_SA_3_2 <- glmer(models(outcome = "SA_y", predictor = "Asthma_medications_2w_total",
                                  variables = var_mod_1, var_added = NULL), 
                           family = binomial, data = dataset %>% filter(Asthma_medications_2w_total > 0), nAGQ = 0)

tab_model(Nomedication_SA_3_1, Nomedication_SA_3_2)
```

# 4.4. Recent active asthma and SA
```{r}
SA_recent_active_asthma_0 <- glmer(models(outcome = "SA_y", predictor = "recent_active_asthma", 
                             variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                      family = binomial, data = dataset, nAGQ = 0)

SA_recent_active_asthma_1 <- glmer(models(outcome = "SA_y", predictor = "recent_active_asthma", variables = var_mod_1, var_added = NULL), 
                      family = binomial, data = dataset, nAGQ = 0)

SA_recent_active_asthma_2 <- glmer(models(outcome = "SA_y", predictor = "recent_active_asthma", variables = var_mod_2, var_added = NULL), 
                      family = binomial, data = dataset, nAGQ = 0)

SA_recent_active_asthma_3 <- glmer(models(outcome = "SA_y", predictor = "recent_active_asthma", variables = var_mod_3, var_added = NULL), 
                      family = binomial, data = dataset, nAGQ = 0)

SA_recent_active_asthma_4 <- glmer(models(outcome = "SA_y", predictor = "recent_active_asthma", variables = var_mod_3, var_added = "scale(cbcl_scr_syn_totprob_r)"), 
                      family = binomial, data = dataset, nAGQ = 0)

tab_model(SA_recent_active_asthma_0, SA_recent_active_asthma_1, SA_recent_active_asthma_2, SA_recent_active_asthma_3, SA_recent_active_asthma_4)
```

# 5. SUICIDE IDEATION
# 5.1. Outcome suicide IDEATION - asthma

```{r}
SI_diag_0 <- glmer(models(outcome = "SI_y", predictor = "asthma_diagnosis_l", 
                                variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                         family = binomial, data = dataset, nAGQ = 0)

SI_diag_1 <- glmer(models(outcome = "SI_y", predictor = "asthma_diagnosis_l", variables = var_mod_1, var_added = NULL), 
                         family = binomial, data = dataset, nAGQ = 0)

SI_diag_2 <- glmer(models(outcome = "SI_y", predictor = "asthma_diagnosis_l", variables = var_mod_2, var_added = NULL), 
                         family = binomial, data = dataset, nAGQ = 0)

SI_diag_3 <- glmer(models(outcome = "SI_y", predictor = "asthma_diagnosis_l", variables = var_mod_3, var_added = NULL), 
                         family = binomial, data = dataset, nAGQ = 0)

SI_diag_4 <- glmer(models(outcome = "SI_y", predictor = "asthma_diagnosis_l", variables = var_mod_3, var_added = "scale(cbcl_scr_syn_totprob_r)"), 
                         family = binomial, data = dataset, nAGQ = 0)

# SI_diag_4_black <- glmer(models(outcome = "SI_y", predictor = "asthma_diagnosis_l", 
#                                       variables = var_mod_3[var_mod_3 != "race_black" & var_mod_3 != "race_white"], 
#                                       var_added = "scale(asthma_PRS)"), family = binomial, data = dataset %>% filter(genetic_afr == 1),
#                                nAGQ = 0)
# 
# SI_diag_4_white <- glmer(models(outcome = "SI_y", predictor = "asthma_diagnosis_l", 
#                                       variables = var_mod_3[var_mod_3 != "race_black" & var_mod_3 != "race_white"], 
#                                       var_added = "scale(asthma_PRS)"), family = binomial, data = dataset %>% filter(genetic_afr == 0),
#                                nAGQ = 0)
# 
# SI_diag_5 <- glmer(models(outcome = "SI_y", predictor = "asthma_diagnosis_l", variables = var_mod_3, 
#                                 var_added = "scale(asthma_PRS)"), family = binomial, data = dataset,
#                          nAGQ = 0)

comb_SI_diag_1 <- tab_model(SI_diag_0, SI_diag_1, SI_diag_2, SI_diag_3, SI_diag_4)
comb_SI_diag_1
```


```{r}
SI_attack_0 <- glmer(models(outcome = "SI_y", predictor = "asthma_attack_l",
                                  variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL),
                           family = binomial, data = dataset, nAGQ = 0)

SI_attack_1 <- glmer(models(outcome = "SI_y", predictor = "asthma_attack_l", variables = var_mod_1, var_added = NULL),
                           family = binomial, data = dataset, nAGQ = 0)

SI_attack_2 <- glmer(models(outcome = "SI_y", predictor = "asthma_attack_l", variables = var_mod_2, var_added = NULL),
                           family = binomial, data = dataset, nAGQ = 0)

SI_attack_3 <- glmer(models(outcome = "SI_y", predictor = "asthma_attack_l", variables = var_mod_3, var_added = NULL),
                           family = binomial, data = dataset, nAGQ = 0)

SI_attack_4 <- glmer(models(outcome = "SI_y", predictor = "asthma_attack_l", variables = var_mod_3, var_added = "scale(cbcl_scr_syn_totprob_r)"),
                           family = binomial, data = dataset, nAGQ = 0)

# SI_attack_4_black <- glmer(models(outcome = "SI_y", predictor = "asthma_attack_l", 
#                                         variables = var_mod_3[var_mod_3 != "race_black" & var_mod_3 != "race_white"],
#                                         var_added = "asthma_PRS"),  family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)
# 
# SI_attack_4_white <- glmer(models(outcome = "SI_y", predictor = "asthma_attack_l", 
#                                         variables = var_mod_3[var_mod_3 != "race_black" & var_mod_3 != "race_white"],
#                                         var_added = "asthma_PRS"),  family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)
# 
# SI_attack_4 <- glmer(models(outcome = "SI_y", predictor = "asthma_attack_l", variables = var_mod_3,
#                                   var_added = "asthma_PRS"),  family = binomial, data = dataset, nAGQ = 0)

comb_SI_attack_1 <- tab_model(SI_attack_0, SI_attack_1, SI_attack_2, SI_attack_3, SI_attack_4)
comb_SI_attack_1
```

```{r}
SI_comp_0 <- glmer(models(outcome = "SI_y", predictor = "asthma_composite", 
                                variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                         family = binomial, data = dataset, nAGQ = 0)

SI_comp_1 <- glmer(models(outcome = "SI_y", predictor = "asthma_composite", variables = var_mod_1, var_added = NULL), 
                         family = binomial, data = dataset, nAGQ = 0)

SI_comp_2 <- glmer(models(outcome = "SI_y", predictor = "asthma_composite", variables = var_mod_2, var_added = NULL), 
                         family = binomial, data = dataset, nAGQ = 0)

SI_comp_3 <- glmer(models(outcome = "SI_y", predictor = "asthma_composite", variables = var_mod_3, var_added = NULL), 
                         family = binomial, data = dataset, nAGQ = 0)

SI_comp_4 <- glmer(models(outcome = "SI_y", predictor = "asthma_composite", variables = var_mod_3, var_added = "scale(cbcl_scr_syn_totprob_r)"), 
                         family = binomial, data = dataset, nAGQ = 0)



# SI_comp_4_black <- glmer(models(outcome = "SI_y", predictor = "asthma_composite", 
#                                       variables = var_mod_3[var_mod_3 != "race_black" & var_mod_3 != "race_white"], 
#                                       var_added = "asthma_PRS"),  family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)
# 
# SI_comp_4_white <- glmer(models(outcome = "SI_y", predictor = "asthma_composite", 
#                                       variables = var_mod_3[var_mod_3 != "race_black" & var_mod_3 != "race_white"], 
#                                       var_added = "asthma_PRS"),  family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)
# 
# SI_comp_4 <- glmer(models(outcome = "SI_y", predictor = "asthma_composite", variables = var_mod_3, 
#                                 var_added = "asthma_PRS"),  family = binomial, data = dataset, nAGQ = 0)


comb_SI_comp_1 <- tab_model(SI_comp_0, SI_comp_1, SI_comp_2, SI_comp_3, SI_comp_4)
comb_SI_comp_1
```

# 5.2. Outcome suicide IDEATION - genetic scores

```{r}
SI_gen_0_black <- glmer(models(outcome = "SI_y", predictor = "asthma_PRS",
                                     variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                              family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)

SI_gen_0_white <- glmer(models(outcome = "SI_y", predictor = "asthma_PRS",
                                     variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                              family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)

SI_gen_1_black <- glmer(models(outcome = "SI_y", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                              family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)

SI_gen_1_white <- glmer(models(outcome = "SI_y", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                              family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)

SI_gen_2_black <- glmer(models(outcome = "SI_y", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                              family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)

SI_gen_2_white <- glmer(models(outcome = "SI_y", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                              family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)

SI_gen_3_black <- glmer(models(outcome = "SI_y", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                              family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)

SI_gen_3_white <- glmer(models(outcome = "SI_y", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                              family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)

comb_SI_gen_1 <- tab_model(SI_gen_0_black, SI_gen_0_white, SI_gen_1_black, SI_gen_1_white, SI_gen_2_black, SI_gen_2_white, 
                           SI_gen_3_black, SI_gen_3_white)
comb_SI_gen_1
```

# 5.3. Number of asthma attack and SI #medhx_ss_6l_times_p_l
```{r}
# Among people with asthma attack only
Noattack_SI_1_1 <- glmer(models(outcome = "SI_y", predictor = "medhx_ss_6l_times_p_l",
                                variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                         family = binomial, data = dataset %>% filter(asthma_attack_l == 1), nAGQ = 0)

Noattack_SI_1_2 <- glmer(models(outcome = "SI_y", predictor = "medhx_ss_6l_times_p_l",
                                variables = var_mod_1, var_added = NULL), 
                         family = binomial, data = dataset %>% filter(asthma_attack_l == 1), nAGQ = 0)

Nomedication_SI_1_1 <- glmer(models(outcome = "SI_y", predictor = "Asthma_medications_2w_total",
                                    variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                             family = binomial, data = dataset %>% filter(asthma_attack_l == 1), nAGQ = 0)

Nomedication_SI_1_2 <- glmer(models(outcome = "SI_y", predictor = "Asthma_medications_2w_total",
                                    variables = var_mod_1, var_added = NULL), 
                             family = binomial, data = dataset %>% filter(asthma_attack_l == 1), nAGQ = 0)

tab_model(Noattack_SI_1_1, Noattack_SI_1_2, Nomedication_SI_1_1, Nomedication_SI_1_2)

# Among people with asthma diagnosis only
Noattack_SI_2_1 <- glmer(models(outcome = "SI_y", predictor = "medhx_ss_6l_times_p_l",
                                variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                         family = binomial, data = dataset %>% filter(asthma_diagnosis_l == 1), nAGQ = 0)

Noattack_SI_2_2 <- glmer(models(outcome = "SI_y", predictor = "medhx_ss_6l_times_p_l",
                                variables = var_mod_1, var_added = NULL), 
                         family = binomial, data = dataset %>% filter(asthma_diagnosis_l == 1), nAGQ = 0)

Nomedication_SI_2_1 <- glmer(models(outcome = "SI_y", predictor = "Asthma_medications_2w_total",
                                    variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                             family = binomial, data = dataset %>% filter(asthma_diagnosis_l == 1), nAGQ = 0)

Nomedication_SI_2_2 <- glmer(models(outcome = "SI_y", predictor = "Asthma_medications_2w_total",
                                    variables = var_mod_1, var_added = NULL), 
                             family = binomial, data = dataset %>% filter(asthma_diagnosis_l == 1), nAGQ = 0)

tab_model(Noattack_SI_2_1, Noattack_SI_2_2, Nomedication_SI_2_1, Nomedication_SI_2_2)

# remove 0 asthma attack (for mod1)
Noattack_SI_3_1 <- glmer(models(outcome = "SI_y", predictor = "medhx_ss_6l_times_p_l",
                                variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                         family = binomial, data = dataset %>% filter(medhx_ss_6a_times_p_l > 0), nAGQ = 0)

Noattack_SI_3_2 <- glmer(models(outcome = "SI_y", predictor = "medhx_ss_6l_times_p_l",
                                variables = var_mod_1, var_added = NULL), 
                         family = binomial, data = dataset %>% filter(medhx_ss_6a_times_p_l > 0), nAGQ = 0)

tab_model(Noattack_SI_3_1, Noattack_SI_3_2)

# remove 0 medications (for mod2)
Nomedication_SI_3_1 <- glmer(models(outcome = "SI_y", predictor = "Asthma_medications_2w_total",
                                    variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                             family = binomial, data = dataset %>% filter(Asthma_medications_2w_total > 0), nAGQ = 0)

Nomedication_SI_3_2 <- glmer(models(outcome = "SI_y", predictor = "Asthma_medications_2w_total",
                                    variables = var_mod_1, var_added = NULL), 
                             family = binomial, data = dataset %>% filter(Asthma_medications_2w_total > 0), nAGQ = 0)

tab_model(Nomedication_SI_3_1, Nomedication_SI_3_2)
```
# 5.4. Recent active asthma and SI
```{r}
SI_recent_active_asthma_0 <- glmer(models(outcome = "SI_y", predictor = "recent_active_asthma", 
                                          variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                                   family = binomial, data = dataset, nAGQ = 0)

SI_recent_active_asthma_1 <- glmer(models(outcome = "SI_y", predictor = "recent_active_asthma", variables = var_mod_1, var_added = NULL), 
                                   family = binomial, data = dataset, nAGQ = 0)

SI_recent_active_asthma_2 <- glmer(models(outcome = "SI_y", predictor = "recent_active_asthma", variables = var_mod_2, var_added = NULL), 
                                   family = binomial, data = dataset, nAGQ = 0)

SI_recent_active_asthma_3 <- glmer(models(outcome = "SI_y", predictor = "recent_active_asthma", variables = var_mod_3, var_added = NULL), 
                                   family = binomial, data = dataset, nAGQ = 0)

SI_recent_active_asthma_4 <- glmer(models(outcome = "SI_y", predictor = "recent_active_asthma", variables = var_mod_3, var_added = "scale(cbcl_scr_syn_totprob_r)"), 
                                   family = binomial, data = dataset, nAGQ = 0)

tab_model(SI_recent_active_asthma_0, SI_recent_active_asthma_1, SI_recent_active_asthma_2, SI_recent_active_asthma_3, SI_recent_active_asthma_4)
```
# 6. ASTHMA - PRS
# 6.1. Outcome asthma - genetic scores

```{r}
diag_PRS_0_black <- glmer(models(outcome = "asthma_diagnosis_l", predictor = "asthma_PRS", 
                               variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                      family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)

diag_PRS_0_white <- glmer(models(outcome = "asthma_diagnosis_l", predictor = "asthma_PRS", 
                               variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                      family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)

diag_PRS_1_black <- glmer(models(outcome = "asthma_diagnosis_l", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                      family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)

diag_PRS_1_white <- glmer(models(outcome = "asthma_diagnosis_l", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                      family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)

attack_PRS_0_black <- glmer(models(outcome = "asthma_attack_l", predictor = "asthma_PRS", 
                               variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                      family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)

attack_PRS_0_white <- glmer(models(outcome = "asthma_attack_l", predictor = "asthma_PRS", 
                               variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                      family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)

attack_PRS_1_black <- glmer(models(outcome = "asthma_attack_l", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                      family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)

attack_PRS_1_white <- glmer(models(outcome = "asthma_attack_l", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                      family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)

comp_PRS_0_black <- glmer(models(outcome = "asthma_attack_l", predictor = "asthma_PRS", 
                               variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                      family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)

comp_PRS_0_white <- glmer(models(outcome = "asthma_attack_l", predictor = "asthma_PRS", 
                               variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                      family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)

comp_PRS_1_black <- glmer(models(outcome = "asthma_composite", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                      family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)

comp_PRS_1_white <- glmer(models(outcome = "asthma_composite", predictor = "asthma_PRS", 
                                     variables = var_mod_1[var_mod_1 != "race_black" & var_mod_1 != "race_white"], var_added = NULL), 
                      family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)

comb_asthma_1 <- tab_model(diag_PRS_0_black, diag_PRS_0_white, diag_PRS_1_black, diag_PRS_1_white, 
                           attack_PRS_0_black, attack_PRS_0_white, attack_PRS_1_black, attack_PRS_1_white,
                           comp_PRS_0_black, comp_PRS_0_white, comp_PRS_1_black, comp_PRS_1_white)
comb_asthma_1
```

# 6.2. Outcome broken bones - asthma genetic scores #medhx_6a_l

```{r}
bb_1_black <- glmer(models(outcome = "medhx_6a_l", predictor = "asthma_PRS",
                            variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                        family = binomial, data = dataset %>% filter(genetic_afr == 1), nAGQ = 0)

bb_1_white <- glmer(models(outcome = "medhx_6a_l", predictor = "asthma_PRS",
                            variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                        family = binomial, data = dataset %>% filter(genetic_afr == 0), nAGQ = 0)

comb_bb_1 <- tab_model(bb_1_black, bb_1_white)
comb_bb_1
```

```{r}
# Recently active asthma was considered for all participants that endorsed at least one of the following items at the 1-year follow-up assessment: having been to the doctor since the baseline assessment for asthma (variable medhx_2a_l asthma_diagnosis_l) or for asthma attack (variable medhx_6l_l asthma_attack_l)
```

# 7. ASTHMA DIAGNOSIS - MEDICATION
```{r}
diag_med_0 <- glmer(models(outcome = "asthma_diagnosis_l", predictor = "Asthma_medications_2w", 
                             variables = "(1 | site_id_l_br/rel_family_id/src_subject_id)", var_added = NULL), 
                      family = binomial, data = dataset, nAGQ = 0)

diag_med_1 <- glmer(models(outcome = "asthma_diagnosis_l", predictor = "Asthma_medications_2w", 
                             variables = var_mod_1, var_added = NULL), 
                      family = binomial, data = dataset, nAGQ = 0)

tab_model(diag_med_0, diag_med_1)
```





